\chapter{Conclusion}\label{chp:conclusion}


The implication of the results in this report is that in order to achieve a higher MMS guarantee in the Mixed Goods setting for homogenous cake, one could possible apply a indivisible algorithm with a higher MMS-guarantee, where the highest MMS approximation guarantee so far is $\frac{3}{4}+\frac{1}{12n}$ \cite{best-mms}. The benefit here being that a very simple algorithm that performs just as well as, or close to, a complex algorithm can be considered a better, or more appliable algorithm. 

In the MMS article \cite{mms} Section 4.4, improving the MMS-guarantee of the mixed algorithm is considered by using a similar logic. However their theorem implies a that a MMS-guarantee algorithm for indivisible goods can be used to achieve a approximate similar allocation for mixed instances. My results indicate however that if such an algorithm exists, then this algorithm can be used directly so solve a mixed instance with the same MMS-guarantee. However any firm conclusions should not be drawn from the experiments presented until proper and general proof is presented.

Not many conclusions can be drawn from the runtime analysis either as this analysis is too limited. The analysis also isn't fair as the indivisible algorithm\cite{Allocations} includes handling of cardinality constraints. In order for a runtime analysis to be completely fair both/all algorithms should solve the same problem.

\clearpage
\input{content/Conclusion/future-work.tex}