\chapter{Introduction}\label{chp:introduction}


While the problem of fairly allocating indivisible items and divisible items have been thoroughly analysed in different settings for each of them, the work done for instances with both divisible and indivisible goods, termed mixed goods, is not yet as thoroughly researched. Instances for only divisible and indivisible resources are easy to imagine. For instance fairly allocating posessions, gifts and resources, or fairly dividing a cake, money or land. Mixed goods instances isn't as obvious, but examples of instances where mixed goods are relevant would be dividing possessions and money, dividing a plot of land with buildings, or different activities over time.

The basis for this project is to focus on algorithms that use the MaxiMinShare fairness goal in order to achieve fair allocations, and then use these algorithms and compare them to "simpler" algorithms for indivisible goods, where the research is more thorough. The goal is to find out if the algorithms for indivisible goods can be used for mixed goods, and if so, how well they perform.


This report will look at various approaches and algorithms proposed in the relevant literature for how to handle a mixed goods setting. In \autoref{sec:preliminaries} we will define the problem and the terminology used in the report. In \autoref{sec:previous-work} we will look at the relevant literature and the different approaches that have been proposed. In \autoref{chp:method} we will present the approach used to compare and analyze these different approaches. In \autoref{chp:results} we will present the experiments we have conducted and the results we have obtained. Finally, in \autoref{chp:conclusion} we will conclude the report and discuss future work.

\input{content/Introduction/preliminairies}
\input{content/Introduction/problem-instance.tex}
\input{content/Introduction/previous-work}